The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
Shorten some text to focus on what is new.

@@

\item \texttt{step-74} SIPG for the Poisson equation \todo[inline]{TODO}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simplified implementation for face integrals}
\label{subsec:feinterfacevalues}
Discontinuous Galerkin (DG) methods -- and other methods with penalty
terms defined on faces -- require the evaluation of averages and jumps
accross cell faces, involving values and derivatives of the shape
functions and solutions from two adjacent cells. The
\texttt{FEInterfaceValues} class, first introduced in \dealii{} 9.2,
is designed to provide the necessary interface.

Internally, this class provides an abstraction for two
\texttt{FEFaceValues} objects (or \texttt{FESubfaceValues} when using
adaptive refinement). The class introduces new interface degrees of
freedom indices that are the union of the degrees of freedom indices
of the two \texttt{FEFaceValues} objects. The interface degrees of
freedom indices can be converted to the corresponding local degrees of
freedom indices of the two cells using a helper function. New in the
current release is better support for vector-valued problems: scalar
or vector components of shape functions can now be extracted by providing an \texttt{FEValuesExtractors} object.

@@

\item \texttt{step-74} implements the symmetric interior penalty Galerkin 
(SIPG) method for Poisson's equation using the \texttt{FEInterfaceValues} class
within the \texttt{MeshWorker::mesh\_loop()} framework. This tutorial demonstrates a
simple to assemble face integrals.
